Analysis Stand Features 

### 2017-05-15 analysis/analysis_stand_features.Rmd
update focal tree

# Get only focal trees  
ft <- tree %>% 
  filter(sp=='Focal') %>% 
  filter(id_focal!='Fresno')

@@

>>>>

# Get only focal trees  
ft <- tree %>% 
  filter(sp=='Focal') %>% 
  filter(id_focal!='Fresno') %>% 
  mutate(site = as.factor(site))

@@

# Focal tree summary

```{r}
## Comparison 
# Select only variables to compare 
ft_sel <- ft %>%
  mutate(dn = dn_mm / 1000, 
         h = height_cm / 100) %>% 
  dplyr::select(dn, h, site)

# Get vector with variables 
variables <- c('dn','h')

  # apply comparison
  out_compara <- compara(df=ft_sel, mivariable = i)

# Loop to export into txt files (see ./out/anovas_ft ... )
for (i in variables){

  file_out <- file(paste0(di,'out/anovas_ft/aov_', i, '.txt'), "w")
  sink(file_out)

### dn Focal tree

```{r, echo=FALSE}
mivariable <- 'dn'
s <- get(paste0('aov_', mivariable))

### height Focal tree

```{r, echo=FALSE}
mivariable <- 'h'
s <- get(paste0('aov_', mivariable))
